---
title: "rm_anova_analysis2"
author: "Nick Fox"
date: "Friday, February 27, 2015"
output: html_document
---

```{r echo = FALSE}
library(dplyr)
library(ggplot2)
library(broom)
#load packages
```


```{r echo = FALSE}

wram_raw <- read.csv("one_platform_wram_raw.csv", header = TRUE)

wram_raw_male <- wram_raw %>%
  filter(Sex != "Female")
#makes male only dataframe

wram_raw_female <- wram_raw %>%
  filter(Sex != "Male")
#makes female only dataframe

wram_raw_female2 <- wram_raw_female %>%
  dplyr::group_by(Day, Animal) %>%
  dplyr::mutate(avr.latency = mean(Duration), avr.distance = mean(Distance)) %>%
  distinct(avr.latency, avr.distance)
#create a new data frame with average latency and average distance travelled by treatment for females

wram_raw_male2 <- wram_raw_male %>%
  dplyr::group_by(Day, Animal) %>%
  dplyr::mutate(avr.latency = mean(Duration), avr.distance = mean(Distance)) %>%
  distinct(avr.latency, avr.distance)
#create a new data frame with average latency and average distance travelled by treatment for males

```


This next set of analyses comes from averaging the data by treatment per day.  Each treatment (SEA or Saline) has 1 point per day.  That point is the average of all of the measures made for the animals of that treatment that day.

#Females - Average Distance Travelled

```{r echo = FALSE}

wram_raw_female2 %>%
  ggplot(aes(x = Day, y = avr.distance, group = Treatment, colour = Treatment)) + ylab("Average distance travelled (m)")+ geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2")
#graph the average distance by treatment

aov.out.F.avrdistance <- aov(avr.distance ~ Treatment * Day + Error(Animal), data = wram_raw_female2)
summary(aov.out.F.avrdistance)
#repeated measures anova for distance (females) using average distance by treatment

```
#Females - Average latency to find platform

```{r echo = FALSE}

wram_raw_female2 %>%
  ggplot(aes(x = Day, y = avr.latency, group = Treatment, colour = Treatment)) + ylab("Average latency to find platform (s)") + geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2")
#graph the average latency by treatment

aov.out.F.avrlatency <- aov(avr.latency ~ Treatment * Day + Error(Animal), data = wram_raw_female2)
summary(aov.out.F.avrlatency)
#repeated measures anova for duration (females) using average latency by treatment
```

#Males - Average Distance Travelled

```{r echo = FALSE}

wram_raw_male2 %>%
  ggplot(aes(x = Day, y = avr.distance, group = Treatment, colour = Treatment)) + ylab("Average distance travelled (m)")+ geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2")
#graph the average distance by treatment

aov.out.M.avrdistance <- aov(avr.distance ~ Treatment * Day + Error(Animal), data = wram_raw_male2)
summary(aov.out.M.avrdistance)
#repeated measures anova for distance (females) using average distance by treatment
```

#Males - Average latency to find platform

```{r echo = FALSE}

wram_raw_male2 %>%
  ggplot(aes(x = Day, y = avr.latency, group = Treatment, colour = Treatment)) + ylab("Average latency to find platform (s)") + geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2")
#graph the average latency by treatment

aov.out.M.avrlatency <- aov(avr.latency ~ Treatment * Day + Error(Test/(Treatment * Day)), data = wram_raw_male2)
summary(aov.out.M.avrlatency)
```
