---
title: "rm_anova_analysis2"
author: "Nick Fox"
date: "Friday, February 27, 2015"
output: html_document
---

```{r echo = FALSE}
library(dplyr)
library(ggplot2)
library(broom)
#load packages
```


```{r echo = FALSE}

wram_raw <- read.csv("one_platform_wram_raw.csv", header = TRUE)

se <- function(x) sqrt(var(x)/length(x))
#adds a function to make standard error calculations (for error bars)

wram_raw_male <- wram_raw %>%
  filter(Sex != "Female")
#makes male only dataframe

wram_raw_female <- wram_raw %>%
  filter(Sex != "Male")
#makes female only dataframe

wram_raw_female2 <- wram_raw_female %>%
  dplyr::group_by(Day, Animal) %>%
  dplyr::mutate(avr.latency = mean(Duration), avr.distance = mean(Distance)) %>%
  distinct(avr.latency, avr.distance)
#create a new data frame with average latency and average distance travelled per female per day (averaged trials)

wram_raw_male2 <- wram_raw_male %>%
  dplyr::group_by(Day, Animal) %>%
  dplyr::mutate(avr.latency = mean(Duration), avr.distance = mean(Distance)) %>%
  distinct(avr.latency, avr.distance)
#create a new data frame with average latency and average distance travelled per male per day (averaged trials)

wram_raw_female3 <- wram_raw_female2 %>%
  dplyr::group_by(Day, Treatment) %>%
  dplyr::mutate(mean.treatment.latency = mean(avr.latency), sd.treatment.latency = sd(avr.latency), sem.treatment.latency = se(avr.latency), mean.treatment.distance = mean(avr.distance), sd.treatment.distance = sd(avr.distance), sem.treatment.distance = se(avr.distance))
#made a new dataframe with mean, std, and SEM calculated by animal x day and by treatment x day
##avr.latency and avr.distance are animal by day. ##mean.latency and mean.distance are treatment

wram_raw_male3 <- wram_raw_male2 %>%
  dplyr::group_by(Day, Treatment) %>%
  dplyr::mutate(mean.treatment.latency = mean(avr.latency), sd.treatment.latency = sd(avr.latency), sem.treatment.latency = se(avr.latency), mean.treatment.distance = mean(avr.distance), sd.treatment.distance = sd(avr.distance), sem.treatment.distance = se(avr.distance))
#made a new dataframe with mean, std, and SEM calculated by animal x day and by treatment x day
##avr.latency and avr.distance are animal by day. ##mean.latency and mean.distance are treatment

```


This next set of analyses comes from averaging the data by treatment per day.  Each treatment (SEA or Saline) has 1 point per day.  That point is the average of all of the measures made for the animals of that treatment that day.

#Females - Average Distance Traveled

```{r echo = FALSE}

wram_raw_female3 %>%
  group_by(Day, Treatment) %>%
  ggplot(aes(x = Day, y = mean.treatment.distance, group = Treatment, colour = Treatment)) + ylab("Average distance travelled (m)")+ geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2") + geom_errorbar(aes(ymin = mean.treatment.distance - sem.treatment.distance, ymax = mean.treatment.distance + sem.treatment.distance), width = 0.1)
#graph the average distance by treatment

aov.out.F.avrdistance <- aov(avr.distance ~ Treatment * Day + Error(Animal), data = wram_raw_female2)
summary(aov.out.F.avrdistance)
#repeated measures anova for distance (females) using average distance by treatment

```
#Females - Average latency to find platform

```{r echo = FALSE}

wram_raw_female3 %>%
  group_by(Day, Treatment) %>%
  ggplot(aes(x = Day, y = mean.treatment.latency, group = Treatment, colour = Treatment)) + ylab("Average latency to find platform (s)") + geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2") + geom_errorbar(aes(ymin = mean.treatment.latency - sem.treatment.latency, ymax = mean.treatment.latency + sem.treatment.latency), width = 0.1)
#graph the average latency by treatment

aov.out.F.avrlatency <- aov(avr.latency ~ Treatment * Day + Error(Animal), data = wram_raw_female2)
summary(aov.out.F.avrlatency)
#repeated measures anova for duration (females) using average latency by treatment
```

#Males - Average Distance Traveled

```{r echo = FALSE}

wram_raw_male3 %>%
    group_by(Day, Treatment) %>%
    ggplot(aes(x = Day, y = mean.treatment.distance, group = Treatment, colour = Treatment)) + ylab("Average distance travelled (m)")+ geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2") + geom_errorbar(aes(ymin = mean.treatment.distance - sem.treatment.distance, ymax = mean.treatment.distance + sem.treatment.distance), width = 0.1)
#graph the average distance by treatment

aov.out.M.avrdistance <- aov(avr.distance ~ Treatment * Day + Error(Animal), data = wram_raw_male2)
summary(aov.out.M.avrdistance)
#repeated measures anova for distance (females) using average distance by treatment
```

#Males - Average latency to find platform

```{r echo = FALSE}

wram_raw_male3 %>%
    group_by(Day, Treatment) %>%
  ggplot(aes(x = Day, y = mean.treatment.latency, group = Treatment, colour = Treatment)) + ylab("Average latency to find platform (s)") + geom_point(size = 4) + geom_line(size = 1) + scale_color_brewer(palette="Dark2") + geom_errorbar(aes(ymin = mean.treatment.latency - sem.treatment.latency, ymax = mean.treatment.latency + sem.treatment.latency), width = 0.1)
#graph the average latency by treatment

aov.out.M.avrlatency <- aov(avr.latency ~ Treatment * Day + Error(Animal), data = wram_raw_male2)
summary(aov.out.M.avrlatency)
```





```{r}
wram_raw_female3 <- wram_raw_female2 %>%
  dplyr::group_by(Day, Treatment) %>%
  dplyr::mutate(mean.latency = mean(avr.latency), sd.latency = sd(avr.latency), sem.latency = se(avr.latency), mean.distance = mean(avr.distance), sem.distance = se(avr.distance))
```