---
title: "single_platform_wram"
author: "Nick Fox"
date: "Wednesday, February 25, 2015"
output: html_document
---





First I loaded in the data.
The dummy code is: 

Treatment: SEA = 1, SAL = 0.  
Sex: Female = 1, Male = 0.

```{r echo = FALSE}
library(dplyr)
library(ggplot2)
library(broom)
setwd("~/GitHub/single_platform_wram")

wram_raw <- read.csv("one_platform_wram_raw.csv", header = TRUE)
wram_raw <- tbl_df(wram_raw)

wram_raw2 <- wram_raw %>%
  group_by(Animal, Treatment, Day) %>%
  mutate(avr_distance = mean(Distance)) %>%
  mutate(avr_latency = mean(Duration))
```


# Distance Travelled by Day #

```{r echo = FALSE}
wram_raw %>%
  ggplot(aes(x = Day, y = Distance, group = Treatment, colour = Treatment)) + geom_jitter()

```

### Then I ran a linear regression on the data and fit the regression line. ###

```{r echo = FALSE}
lm2 <- lm(Distance ~ Day + Treatment + Sex + Day:Treatment, data = wram_raw)
summary(lm2)
```

```{r echo = FALSE}
wram_raw %>%
  ggplot(aes(x = Day, y = Distance, group = Treatment, colour = Treatment)) + geom_jitter(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE, size = 1)
```


As you can see from the summary of the regression model, there is a **significant main effect of day** on total distance travelled in the wRAM.  We did not detect an effect of SEA treatment or Sex.



-----
-----


Here is the same information using the average of the four trials each day, so each animal has 1 measurement per day.

```{r echo = FALSE}
wram_raw2 %>%
  distinct(Animal, avr_distance) %>%
  ggplot(aes(x = Day, y = avr_distance, group = Treatment, colour = Treatment)) + geom_jitter(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE, size = 1)
```

```{r echo = FALSE}
wram_raw3 <- wram_raw2 %>%
  distinct(Animal, avr_distance)
```


I ran a regresson on this data as well, but the results are exactly the same (as you would expect)
```{r echo = FALSE}
lm4 <- lm(avr_distance ~ Day + Treatment + Sex + Day:Treatment, data = wram_raw3)

summary(lm4)
```



-----
-----


# Latency to Reach Platform (Duration) by Day #

```{r echo = FALSE}
wram_raw %>%
  ggplot(aes(x = Day, y = Duration, group = Treatment, colour = Treatment)) + geom_jitter()

```

### the linear regression of duration on day and the regression line: ###

``` {r echo = FALSE}
lm3 <- lm(Duration ~ Day + Treatment + Sex + Day:Treatment, data = wram_raw)
summary(lm3)
```

```{r echo = FALSE}
wram_raw %>%
  ggplot(aes(x = Day, y = Duration, group = Treatment, colour = Treatment)) + geom_jitter(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE, size = 1)
```

As you can see from the summary of the regression model, there is a **significant main effect of day**  and a **significant main effect of sex (females took less time to find the platform)**.  We did not detect an effect of treatment.

-----
-----
Here is the same information using the average of the four trials each day, so each animal has 1 measurement per day.

```{r echo = FALSE}
wram_raw2 %>%
  distinct(Animal, avr_latency) %>%
  ggplot(aes(x = Day, y = avr_latency, group = Treatment, colour = Treatment)) + geom_jitter(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE, size = 1)
```

And here is the regression on this averaged latency data:

```{r echo = FALSE}
wram_raw4 <- wram_raw2 %>%
  distinct(Animal, avr_latency)
```

```{r echo = FALSE}
lm5 <- lm(avr_latency ~ Day + Treatment + Sex + Day:Treatment, data = wram_raw4)

summary(lm5)
```

The regression output is the same for the averaged data as it is for the whole data.